---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```


DHSC Colours R package
## Features
 - DHSC branded powerpoint template for rmarkdown.
 - Approved colour codes for DHSC outputs.
 - Colourblind friendly options
 - GGplot theme for consistant outputs
 - GGplot fill and colour scales using dhsc branding colours.
 - Shortcut function remove y axis padding so intercept can be 0.
 - DHSC_table function for left aligned tables in markdown. 


## Installation

Install using devtools: ```devtools::install_github("https://github.com/DataS-DHSC/DHSC_colours")```


## Branded powerpoint template

Installing this package will install the template for a DHSC
branded powerpoint in rmarkdown. Accessed from within rstudio via:
*File > New File > R Markdown > From Template > DHSC Powerpoint*


## Colour Codes

The function ```dhsc_colours()``` will return a named list of the approved
colours. Each individual colour can also be called by it's helper function.
For example: ```dhsc_dark_blue()```. There are approved shades of black, white
and grey, which are retrieved via ```dhsc_bw()```

Having access to the individual colour codes like this will allow users to quickly
format whatever vizualisation library they are using to align with the DHSC palette.

## Colourblind friendly palettes 

Three and four colour accesible pallets have been hard coded into this package. 
You can retrieve the colour selections with ```DHSC_accessible_3()``` and 
```DHSC_accessible_4()```. Or you can use them directly with your ggplots via 
```DHSC_accessible_scales()```.

## GGplot theme

There is a ggplot theme which you can include with any ggplot to standardise on a 
consistant aesthetic. The theme is accessed via ```theme_dhsc()``` and can be
included in any ggplot with ```+theme_dhsc()```

## GGplot colour and fill scales

There are also some colour scales which you can ```+``` on to a ggplot object 
to recolour it with DHSC colours. There are separate scales for continuous and discrete variables.

## Shortcut to set y axis intercept to 0. 

By default, ggplot adds a 5% padding to your data when creating a y axis, this is
to ensure that your data don't sit directly on the axis line. However it is not
always desirable, e.g. with bar plots. Adding ```+zero_y_padding()``` to your
ggplot objects will remove the padding, improving the way some plots appear. 

## DHSC tables

By default, numeric columns in rmarkdown can appear right aligned (excel style).
The ```DHSC_table()``` function removes this behaviour and aligns all table text
to the left.

## Example Plots

```{r examples, message=FALSE}
library(dplyr)
library(ggplot2)
library(DHSCcolours)

#Barplot with 3 bars with a discrete X axis filled with DHSC colours
sim_series(3)%>%
  ggplot(aes(x=X, y=Z, fill=X))+
  geom_col()+
  DHSCcolours::scale_fill_dhsc_d()+
  theme_dhsc()+
  ggtitle("scale_fill_dhsc_d")+
  zero_y_padding()
  
#Barplot with 4 bars with a discrete X axis filled with accesible colours
sim_series(4)%>%
  ggplot(aes(x=X, y=Z, fill=X))+
  geom_col()+
  DHSCcolours::DHSC_accessible_scales(4)+
  theme_dhsc()+
  ggtitle("scale_fill_dhsc_d")+
  zero_y_padding()

#Barplot with 25 bars with a discrete X axis filled with DHSC colours
sim_series(25)%>%
  ggplot(aes(x=X, y=Z, fill=X))+
  geom_col()+
  DHSCcolours::scale_fill_dhsc_d()+
  theme_dhsc()+
  ggtitle("scale_fill_dhsc_d")+
  zero_y_padding()
  
#Barplot with 25 bars with a continuous X axis with DHSC primary green - purple fill
sim_series(25)%>%
  ggplot(aes(x=Y, y=Z, fill=Z))+
  geom_col()+
  scale_fill_dhsc_c()+
  theme_dhsc()+
  ggtitle("scale_fill_dhsc_c")+
  zero_y_padding()

#Barplot with 25 bars with a continuous X axis with red green fill
sim_series(25)%>%
  ggplot(aes(x=Y, y=Z, fill=Z))+
  geom_col()+
  scale_fill_dhsc_red_green_c()+
  theme_dhsc()+
  ggtitle("scale_fill_dhsc_red_green_c")+
  zero_y_padding()

#Barplot with 25 bars with a continuous X axis with blue green fill
sim_series(25)%>%
  ggplot(aes(x=Y, y=Z, fill=Z))+
  geom_col()+
  scale_fill_dhsc_blue_green_c() +
  theme_dhsc()+
  ggtitle("scale_fill_dhsc_blue_green_c")+
  zero_y_padding()

#Barplot with 25 bars with a continuous X axis with blue yellow fill
sim_series(25)%>%
  ggplot(aes(x=Y, y=Z, fill=Z))+
  geom_col()+
  scale_fill_dhsc_blue_yellow_c() +
  theme_dhsc()+
  ggtitle("scale_fill_dhsc_blue_yellow_c")+
  zero_y_padding()

```
